Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-12-05 papers/thesis-kirstie/thesis.tex
edits
edit

Besides changing the width of the Gaussians, there is another way to 
generate different number density profiles for a given number density.
It may be that not all lattice sites are occupied. Vacancies can be taken 
into account while keeping the overall number density the same by 
making the cells smaller. A large collection of smaller cells creates a 
new number density profile shown in Figure~\ref{fig:Ensemble_Smallcells} 
with eight smaller Gaussians each of which is now one-eighth the height. 
Instead of thinking of an atom in one of the eight small cells, the same 
Gaussian distribution can be obtained from thinking of one-eighth of an 
atom in each small cell as shown in Figure~\ref{fig:SameStatPic}. 
This makes it convenient to describe the new 
number density in terms of the fraction of vacancies, $f_v$. 
The resulting number density is then given by
\begin{align}
    n = (1-f_v){n_{no.vacancies}}
\end{align}

@@

\begin{displaymath}\text{Input:~~~~~~~~~~~~~~~~~~~~~~~~~~~T,~~ n,~~Range of fv,~~Range of gw~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
\begin{displaymath}\text{Set:~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~N~=~1~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
\begin{displaymath}\text{Best}\left(\frac{F}{N}\right)_{diff}= 1e100\end{displaymath}
Loop: 
\begin{displaymath}\text{fv = one of the fv values from input}\end{displaymath}
\begin{equation}N_{primitive.cell}=(1-\text{fv})\text{N}\end{equation}
\begin{equation}V_{primitive.cell}=\frac{\text{1}}{\text{n}}(1-\text{fv})\text{N}\end{equation}
\begin{displaymath}\sigma = \text{one of the gw values from input}\end{displaymath}
\begin{equation}{n(r)=\frac{1}{\left(\sqrt{2\pi}\sigma\right)^3}\int\exp^{-\frac{|\vec{r}-\vec{R}|^2}{2\sigma^2}}d\vec{r}}\end{equation} 
\begin{equation}\left(\frac{F}{N}\right)_{crystal}=\frac{cFideal_{primitive.cell} + cFexcess_{primitive.cell}}{N_{primitive.cell}}\end{equation}
\begin{equation}\left(\frac{F}{N}\right)_{liquid}=\frac{lFideal_{primitive.cell} + lFexcess_{primitive.cell}}{N_{primitive.cell}}\end{equation}
\begin{equation}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{crystal}-{~~}\left(\frac{F}{N}\right)_{liquid}\end{equation}
\begin{displaymath}\text{If~~~~~~}\left(\frac{F}{N}\right)_{diff}<\text{~~~~Best}\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Then~~~~~~}\text{Best}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Output:~~~~~~~~~~~~ Best}\left(\frac{F}{N}\right)_{crystal}\text{~~and~~~~~~}\left(\frac{F}{N}\right)_{liquid}\text{~~~~for the given T, n ~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath}

>>>>

Besides changing the width of the Gaussians, there is another way to 
generate different number density profiles for a given number density.
It may be that not all lattice sites are occupied. Vacancies can be taken 
into account while keeping the overall number density the same by 
making the cells smaller. A large collection of smaller cells creates a 
new number density profile shown in Figure~\ref{fig:Ensemble_Smallcells} 
with eight smaller Gaussians each of which is now one-eighth the height. 
Instead of thinking of an atom in one of the eight small cells, the same 
Gaussian distribution can be obtained from thinking of one-eighth of an 
atom in each small cell as shown in Figure~\ref{fig:SameStatPic}.  
The number of particles within a primitive cell is then given by  
\begin{align}
    N= (1-f_v){N_{no.vacancies}}
\end{align}

@@

\begin{displaymath}\text{Input:~~~~~~~~~~~~~~~~~~~~~~~~~~~T,~~ n,~~Range of fv,~~Range of gw~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
\begin{displaymath}\text{Set:~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~N~=~1~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath} 
\begin{displaymath}\text{Best}\left(\frac{F}{N}\right)_{diff}= 1e100\end{displaymath}
\begin{displaymath}\text{lattice constant}=\left(\frac{4(1-f_v)}{n}\right)^{\frac{1}{3}}\end{displaymath}
The number of atoms in one primitive cell is one, $N_{primitive.cell}=1$.

Loop: 
\begin{displaymath}\text{fv = one of the fv values from input}\end{displaymath}
\begin{equation}N_{primitive.cell}=(1-\text{fv})\text{N}\end{equation}
\begin{equation}V_{primitive.cell}=\frac{\text{1}}{\text{n}}(1-\text{fv})\text{N}\end{equation}
\begin{displaymath}\sigma = \text{one of the gw values from input}\end{displaymath}
\begin{equation}{n(r)=\frac{1}{\left(\sqrt{2\pi}\sigma\right)^3}\int\exp^{-\frac{|\vec{r}-\vec{R}|^2}{2\sigma^2}}d\vec{r}}\end{equation} 
\begin{equation}\left(\frac{F}{N}\right)_{crystal}=\frac{cFideal_{primitive.cell} + cFexcess_{primitive.cell}}{N_{primitive.cell}}\end{equation}
\begin{equation}\left(\frac{F}{N}\right)_{liquid}=\frac{lFideal_{primitive.cell} + lFexcess_{primitive.cell}}{N_{primitive.cell}}\end{equation}
\begin{equation}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{crystal}-{~~}\left(\frac{F}{N}\right)_{liquid}\end{equation}
\begin{displaymath}\text{If~~~~~~}\left(\frac{F}{N}\right)_{diff}<\text{~~~~Best}\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Then~~~~~~}\text{Best}\left(\frac{F}{N}\right)_{diff}=\left(\frac{F}{N}\right)_{diff}\end{displaymath}
\begin{displaymath}\text{Output:~~~~~~~~~~~~ Best}\left(\frac{F}{N}\right)_{crystal}\text{~~and~~~~~~}\left(\frac{F}{N}\right)_{liquid}\text{~~~~for the given T, n ~~~~~~~~~~~~~~~~~~~~~~~~~}\end{displaymath}
